Introducing ICBe: An Event Extraction Dataset from Narratives about International Crises

### 2023-08-04 replication_paper/psrm_draft/ICBe_manuscript.Rmd
fig size fix

\doublespacing

@@

![Cuban Missile Crisis (1962) - ICB Narrative vs. ICBe Events](case_study_cuban_precision.png){#fig-cuba-narrative}

@@

![Dots represent individual ICB narrative sentences, as embedded by the Paraphrase-MPNET-base-v2 large language model and flattened into two dimensions with UMAP. Text labels reflect individual leaves of the ICBe ontology, and colors represent intermediate branches of the ontology. Label placement is the median of all of the sentences that the tag was applied to by the coders. The dendrogram shows hierarchical clustering of the tags. If ICBe precision is high, then the sentences that tags were applied to ought to say similar things and the intended shape of the ontology ought to be visually recognizable.](p_semantic_embeddings_dendro.png){#fig-umap}

@@

![Crisis map for the Cuban Missile Crisis. The start of the crisis is at the top and end of the crisis is the bottom, with each actor in a column with labeled points identifying their speeches, actions, and thoughts.](p_196_icbe.png){#fig-cuba-crisismap}

@@

![The unit of analysis is the dyad-day. Top 10 most active dyads per category shown. Red text shows events from the synthetic narrative relative to that event category. Blue bars indicate an event recorded by ICEWs for that dyad on that day.](p_precision_icews.png){#fig-precision-icews}

@@

This work was supported by a grant from the Office of Naval Research \[N00014-19-1-2491\] and from the Charles Koch Foundation \[20180481\]. The financial sponsors played no in the design, execution, analysis and interpretation of data, or writing of the study.

>>>>

\doublespacing
\newpage

@@

![Cuban Missile Crisis (1962) - ICB Narrative vs. ICBe Events](case_study_cuban_precision.png){#fig-cuba-narrative width="7in" height="8in"}

@@

![Dots represent individual ICB narrative sentences, as embedded by the Paraphrase-MPNET-base-v2 large language model and flattened into two dimensions with UMAP. Text labels reflect individual leaves of the ICBe ontology, and colors represent intermediate branches of the ontology. Label placement is the median of all of the sentences that the tag was applied to by the coders. The dendrogram shows hierarchical clustering of the tags. If ICBe precision is high, then the sentences that tags were applied to ought to say similar things and the intended shape of the ontology ought to be visually recognizable.](p_semantic_embeddings_dendro.png){#fig-umap width="7in" height="7in"}

@@

![Crisis map for the Cuban Missile Crisis. The start of the crisis is at the top and end of the crisis is the bottom, with each actor in a column with labeled points identifying their speeches, actions, and thoughts.](p_196_icbe.png){#fig-cuba-crisismap width="6in"}

@@

![The unit of analysis is the dyad-day. Top 10 most active dyads per category shown. Red text shows events from the synthetic narrative relative to that event category. Blue bars indicate an event recorded by ICEWs for that dyad on that day.](p_precision_icews.png){#fig-precision-icews width="7in" height="5in"}

@@

This work was supported by a grant from the Office of Naval Research $N00014-19-1-2491$ and from the Charles Koch Foundation $20180481$. The financial sponsors played no in the design, execution, analysis and interpretation of data, or writing of the study.

### 2023-08-04 replication_paper/psrm_draft/ICBe_manuscript.tex
fig size fix

\begin{figure}
\hypertarget{fig-cuba-narrative}{%
\centering
\includegraphics{case_study_cuban_precision.png}
\caption{Cuban Missile Crisis (1962) - ICB Narrative vs.~ICBe
Events}\label{fig-cuba-narrative}
}
\end{figure}

@@

\hhline{|>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-|>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-|>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}\endfirsthead \caption[]{Ontological\ coverage\ of\ ICBe\ versus\ existing\ State\ of\ the\ Art}\\

@@

\begin{figure}
\hypertarget{fig-umap}{%
\centering
\includegraphics{p_semantic_embeddings_dendro.png}
\caption{Dots represent individual ICB narrative sentences, as embedded
by the Paraphrase-MPNET-base-v2 large language model and flattened into
two dimensions with UMAP. Text labels reflect individual leaves of the
ICBe ontology, and colors represent intermediate branches of the
ontology. Label placement is the median of all of the sentences that the
tag was applied to by the coders. The dendrogram shows hierarchical
clustering of the tags. If ICBe precision is high, then the sentences
that tags were applied to ought to say similar things and the intended
shape of the ontology ought to be visually
recognizable.}\label{fig-umap}
}
\end{figure}

@@

\begin{figure}
\hypertarget{fig-cuba-crisismap}{%
\centering
\includegraphics{p_196_icbe.png}
\caption{Crisis map for the Cuban Missile Crisis. The start of the
crisis is at the top and end of the crisis is the bottom, with each
actor in a column with labeled points identifying their speeches,
actions, and thoughts.}\label{fig-cuba-crisismap}
}
\end{figure}

@@

\begin{figure}
\hypertarget{fig-precision-icews}{%
\centering
\includegraphics{p_precision_icews.png}
\caption{The unit of analysis is the dyad-day. Top 10 most active dyads
per category shown. Red text shows events from the synthetic narrative
relative to that event category. Blue bars indicate an event recorded by
ICEWs for that dyad on that day.}\label{fig-precision-icews}
}
\end{figure}

@@

This work was supported by a grant from the Office of Naval Research
\[N00014-19-1-2491\] and from the Charles Koch Foundation \[20180481\].
The financial sponsors played no in the design, execution, analysis and
interpretation of data, or writing of the study.

>>>>

\begin{figure}
\hypertarget{fig-cuba-narrative}{%
\centering
\includegraphics[width=7in,height=8in]{case_study_cuban_precision.png}
\caption{Cuban Missile Crisis (1962) - ICB Narrative vs.~ICBe
Events}\label{fig-cuba-narrative}
}
\end{figure}

@@

@@

\begin{figure}
\hypertarget{fig-umap}{%
\centering
\includegraphics[width=7in,height=7in]{p_semantic_embeddings_dendro.png}
\caption{Dots represent individual ICB narrative sentences, as embedded
by the Paraphrase-MPNET-base-v2 large language model and flattened into
two dimensions with UMAP. Text labels reflect individual leaves of the
ICBe ontology, and colors represent intermediate branches of the
ontology. Label placement is the median of all of the sentences that the
tag was applied to by the coders. The dendrogram shows hierarchical
clustering of the tags. If ICBe precision is high, then the sentences
that tags were applied to ought to say similar things and the intended
shape of the ontology ought to be visually
recognizable.}\label{fig-umap}
}
\end{figure}

@@

\begin{figure}
\hypertarget{fig-cuba-crisismap}{%
\centering
\includegraphics[width=6in,height=\textheight]{p_196_icbe.png}
\caption{Crisis map for the Cuban Missile Crisis. The start of the
crisis is at the top and end of the crisis is the bottom, with each
actor in a column with labeled points identifying their speeches,
actions, and thoughts.}\label{fig-cuba-crisismap}
}
\end{figure}

@@

\begin{figure}
\hypertarget{fig-precision-icews}{%
\centering
\includegraphics[width=7in,height=5in]{p_precision_icews.png}
\caption{The unit of analysis is the dyad-day. Top 10 most active dyads
per category shown. Red text shows events from the synthetic narrative
relative to that event category. Blue bars indicate an event recorded by
ICEWs for that dyad on that day.}\label{fig-precision-icews}
}
\end{figure}

@@

This work was supported by a grant from the Office of Naval Research
\(N00014-19-1-2491\) and from the Charles Koch Foundation \(20180481\).
The financial sponsors played no in the design, execution, analysis and
interpretation of data, or writing of the study.
